\large{Vipassana for Hackers} \\ \Huge{Paper Two: The Brain} \\ \large\textit{Version 0.2}

### 2019-10-07 paper-two/paper-two.tex
updating 2nd todo MTL

\subsubsection{Autobiographical memory and future simulations}

@@

The Limbic System is a complex set of structures that lies on both sides of the
Thalamus, just under the Cerebrum. It includes the Hypothalamus, the Hippocampus, the
Amygdala, and several other nearby areas. It appears to be primarily responsible for
our emotional life and has a specific involvement in the formation of memories. \cite{limbic}

The critical role of the MTL in long term memory is well documented. \cite{mtl}
The MTS has also been activated during autobiographical memory retrieval,
contextual association, and semantic knowledge. \cite{defaultnetworkadaptive}

>>>>

\subsubsection{Autobiographical memory and future simulations}
The term "autobiographical memory" refers to our memory for specific episodes, 
and to our conceptual, generic, and schematic knowledge of our lives.

The Medial Temporal Lobe (MTL) which is found on the medial surface of the temporal lobe and plays 
an important role in memory processing. 
The MTL consists of the hippocampal formation on top and the parahippocampal gyrus below it as well as
The entorhinal and perirhinal cortices. 
The MTL along with the amygdala and the olfactory cortex, hypothalamus and several other 
anatomically connected areas forms the limbic system. It appears to be primarily responsible for
our emotional life and has a specific involvement in the formation of memories. \cite{limbic}

@@

The Limbic System is a complex set of structures that lies on both sides of the
Thalamus, just under the Cerebrum. It includes the Hypothalamus, the Hippocampus, the
Amygdala, a
The critical role of the MTL in long term memory is well documented. \cite{mtl}
The MTS has also been activated during autobiographical memory retrieval,
contextual association, and semantic knowledge. \cite{defaultnetworkadaptive}
